\documentclass[11pt]{scrartcl}

\usepackage{cancel}
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
\usepackage[sexy]{evan}

\title{18SLC5}
\author{Himadri Mandal}

\begin{document}
\maketitle

\section{Solution}
Never expected to solve this. Could'nt. Nice problem, however.

The required minimum is $k(4k^2+k-1)/2$.
\bigskip

\textbf{Construction:}
We denote the players $P_1$, \dots, $P_k$
and $Q_1$, \dots, $Q_k$ in general.
In the first $\binom k2$ days,
the players $P_1$, \dots, $P_k$ arrive in order,
and when each player arrives they play everyone else.
The last $\binom k2$ are done in a symmetric way.
In the middle $k^2$ days we have two phases.
First $Q_1$, \dots, $Q_k$ arrive in order;
when $Q_i$ arrives they immediately play $P_1$, \dots, $P_{k+1-i}$.
Then $P_1$, \dots, $P_k$ depart in order;
before $P_i$ departs they play the rest of their matches.

\bigskip

\textbf{Minimality:}
Let us denote the arrival and departure dates by
$$1 = a_1 \geq a_2 \cdots \geq a_{2k} \text{ and } \binom{2k}{2} = b_1 \geq b_2 \geq \cdots \geq b_{2k}$$

Clearly, the total cost is 
\[ S = \sum_n \left( b_n - a_n + 1 \right). \]

\begin{claim*}
	$a_n - 1 \le \binom{n-1}{2}$
	and $\binom{2k}{2} - b_n \le \binom{n-1}{2}$
	for $n = 1 , 2, \dots, k$.
\end{claim*}
\begin{proof}
	Quite obvious, just notice that before $n$ arrives we have at most $n-1$ players. 2nd bound can be derived similarly.
\end{proof}

\begin{claim*}
	For $n > k$ we have
	\[ (a_n - 1) + \left( \binom{2k}{2} - b_n \right)
	\le 2 \binom{n-1}{2} - \binom{2(n-1)-2k}{2} \]
\end{claim*}
\begin{proof}
	The idea of this proof is similar to the previous one.

	However, when $n > k$
	we double-count certain games.
	Specifically, there are $n-1$ players
	that arrive before $a_n$
	and $n-1$ players who depart after $b_n$.
	Therefore, there are at least $2(n-1)-2k$ players' games overcounted.
	This gives us the $\displaymath\binom{2(n-1)-2k}{2}$ term above.
\end{proof}

To finish, note that 
$$S = \sum_{n=1}^{2k}(b_n-a_n+1) \geq \sum_{n=1}^{2k} \lf{\binom{2k}{2}} - 2 \binom{n-1}{2}} + \sum_{n=k+2}^{2k}\binom{2(n-1)-2k}{2}$$
$$= \frac12 k(4k^2+k-1)$$
\end{document}